The origin of cosmic-ray electrons in cluster outskirts

### 2012-02-01 paper.tex
update Method

\def\del#1{{}}
%\def\del#1{{\bf (DELETED TEXT)}}
%\def\C#1{#1}
\def\C#1{{\bf #1}}

@@

However, this then presents a puzzle. Cosmological simulations show that while gas initially undergoes strong shocks (up to $\mach \sim 10^{3}$) accreting onto non-linear structures and filaments, shocks in the ICM and cluster outskirts are relatively modest ($\mach \sim 1-5$), since the gas has already reached sub-keV temperatures \citep{ryu03,pfrommer06,skillman08}. While DSA is efficient in accelerating particles in the thermal Maxwellian tail at high Mach numbers \citep{bell78,drury83}, and as confirmed in observations of supernova remnants \citep{parizot06,reynolds08}, at lower Mach numbers the efficiency of DSA is known to plummet exponentially {\bf SPO: should we include a figure of this? To me this paper is motivated by 2 figures, that of the acceleration efficiency as a function of Mach number and the cooling time as a function of energy---we could put it in 1 figure.} Indeed, in the test-particle regime where suprathermal particles undergo acceleration via a thermal leakage process (which compare well against kinetic DSA simulations) the acceleration efficiency for weak shocks $\mach \sim 3$ is extremely small; the fraction of protons accelerated is $\sim 10^{-4}-10^{-3}$, and cosmic ray proton pressure is $\lsim 1\%$ of the shock ram pressure \citep{kang11}. The acceleration efficiency of electrons at low Mach numbers is likely to be far smaller still. The injection problem for thermal electrons already known to be severe at high Mach numbers, due to the smaller gyroradius of thermal electrons: the relative acceleration efficiency of cosmic ray electrons is lower by $\sim 10^{-2}$ as in the Galaxy \citep{schlickeiser02} or even $\sim 10^{-4}$ as in supernova remnants \citep{morlino09}). These relative efficiencies likely plummets further at low Mach numbers. These considerations appear to contradict the appearance of bright radio relics, and perhaps suggest that our understanding of DSA at low Mach numbers is incomplete (for recent progress, see \citep{gargate12}).

A possible solution is if there is a pre-existing population of cosmic ray electrons with gyroradii comparable or larger than that of the shock thickness. In this case, injection from the thermal pool is no longer an issue \citep{markevitch05,giacintucci08,kang11}; here,  \citet{kang11} show that re-acceleration should dominate over fresh injection. %\footnote{Turbulent re-acceleration, which is thought to operate at lower Mach numbers, also requires a seed population of relativistic particles}. 
DSA has a much larger effect on radio emission than adiabatic compression; including the downstream magnetic field amplification, synchrotron emission could be boosted by a factor $\sim 100-1000$ for $\mach \sim 3$ \citep{kang11}. Thus, the luminosity function of radio gischt will be strongly modified by the presence or absence of a seed relativistic electron population, whose existence has never been directly demonstrated. In this paper, we use our existing high-resolution SPH simulations of cosmic-ray protons in clusters \citep{pinzke10} to infer whether structure formation shocks could generate them\footnote{They could also have a non-gravitational origin, such as AGN injection, though the filling factor at these large radii is likely to be small.}, taking into account the effects of electron cooling. Note that DSA operates identically on relativistic particles of the same rigidity ($R=pc/Ze$), so the injected proton and electron spectrum are the same, modulo their relative acceleration efficiency, which we conservatively calibrate off Galactic observations.%\footnote{Note, however, that at energies where protons are subrelativistic, the electron spectrum has to be obtained from the proton spectrum by extrapolating the latter from the relativistic regime.} 
In the low-density outskirts of clusters, proton loss timescales are several Hubble times, so we can directly derive the injected energy to each SPH CRp particle directly from our existing simulation snapshots and derive an appropriate scaled injection of CR electrons (CRe). Unlike CRp, Coulomb and inverse Compton/synchrotron loss processes are more efficient and have to be taken into account (IC off the CMB, which has an equivalent energy density of $B=3.24 (1+z)^{2} \mu$G, should dominate in the outer regions). We evolve the time-dependent cosmic-ray energy equation to track the evolving distribution function of CRe. In Fig \ref{fig:ensslin}, we can see that the $\sim 10$ GeV CRe  responsible for $\sim$GHz emission in a $\mu$G field has energy loss timescales of $\sim 10^{8}$yr, but a large population of $\sim 100$ MeV electrons could build up. Note that secondary CRe which arise from hadronic interactions of CRp are not thought to be significant at these low densities, though for a dissenting view, see \citet{keshet10}. We calculate the abundance of such seed electrons from structure formation shocks in the cluster outskirts. In general, we find that they are, reaffirming radio gischt as a reliable tracer of large scale shocks and magnetic fields

\begin{figure}[ht]
\begin{center}
%\resizebox{!}{5.5cm}{\includegraphics{./figures/ensslin.eps}}
%%\resizebox{!}{5.5cm}{\includegraphics{ensslin2.pdf}}
%\resizebox{!}{5.0cm}{\includegraphics{circles.pdf}}
%%\hspace{0.05cm}
%%%\vspace{-1cm} 
\end{center}
\caption{Cooling time of CR electrons (left panel) and CR protons (right panel) for typical conditions in the ICM. CRe can only survive for a Hubble time in the underdense outskirts of clusters; $\sim 100$MeV electrons should be the most long-lived. By contrast, CRp above 10 GeV can survive on cosmological timescales. From \citet{ensslin11}. {\bf I stole this figure from EnsslinÉshould we make our own?}}
\label{fig:ensslin} % caption for the whole figure
\end{figure}

@@

\section{Simulations}
\label{sect:simulations}
Our simulations were performed in a $\Lambda$CDM universe using the
cosmological parameters: $\Omega_{\mr m}=\Omega_\DM + \Omega_{\mr
  b}=0.3, \, \Omega_{\mr b}=0.039, \, \Omega_\Lambda=0.7, \, h=0.7, \,
n_{\mr s}=1$, and $\sigma_8=0.9$. The total matter density in units of
the critical density of the universe $\rho_{\rm crit}$ is denoted by
$\Omega_{\mr m}$, the baryonic density by $\Omega_{\mr b}$, the DM
density by $\Omega_\DM$ and the cosmological constant today is denoted
by $\Omega_\Lambda$. The critical density, $\rho_{\rm crit}=3H_0/(8\pi
G)$, where the present day Hubble constant $H_0=100\, h \, \mr{km}\,
\mr{s}^{-1} \, \mr{Myr}^{-1}$. $n_{\mr s}$ represents the spectral
index of the primordial power-spectrum, and $\sigma_8$ denotes the
$rms$ linear mass fluctuation within a sphere of radius $8 \,h^{-1}
\mr{Mpc}$ extrapolated to $z = 0$. The simulations were carried out
with an updated and extended version of the distributed-memory
parallel TreeSPH code GADGET-2 \citep{2005MNRAS.364.1105S,
  2001NewA....6...79S}. Gravitational forces were computed using a
combination of particle-mesh and tree algorithms.  Hydrodynamic forces
are computed with a variant of the smoothed particle hydrodynamics
(SPH) algorithm that conserves energy and entropy where appropriate,
i.e. outside of shocked regions \citep{2002MNRAS.333..649S}.  Our
simulations follow the radiative cooling of the gas, star formation,
supernova feedback, and a photo-ionizing background \citep[details can
  be found in][]{2007MNRAS.378..385P}. We model the cosmic ray (CR)
physics in a self-consistent way \citep{pfrommer06,
  2007A&A...473...41E, 2008A&A...481...33J} and attach a CR proton
distribution function to each SPH fluid element. We include the
adiabatic CR transport process such as compression and rarefaction,
and a number of physical source and sink terms which modify the cosmic
ray pressure of each CR population separately. The most important
sources considered for injection are, diffusive shock acceleration at
cosmological structure formation shocks and shock waves in supernova
remnants, while the primary sinks are thermalization by Coulomb
interactions, and catastrophic losses by hadronization. For
simplicity, in this paper we do not take into account CRs injected
into the inter-stellar medium from supernova remnants (see Pinzke, Oh,
and Pfrommer, in prep. for a discussion of this topic).

@@

\section{Method}
\label{sect:method}
In this section we explain both the method that we use to derive the
CR electron distribution function that builds up during the structure
formation process of galaxy clusters, and the formalism for
calculating synchrotron emission from in galaxy cluster that is
undergoing a merger at low redshifts.

Our scheme is summarized in descending order by the following bullet points:
\begin{itemize}
\item derive CR proton distribution function from each simulation output at different time $t$
\item calculate injected CR proton population between snapshots 
\item convert injected protons to injected electrons
\item evolve each injected CR electron population to a later time $\tend$ by
  accounting for losses (Coulomb, inverse Compton, and adiabatic)
\item add up the CR electron distribution for all SPH particles at time $\tend$
\item re-accelerate CR electron distribution function at time $\tend$
  using typical values for a merging shock in cluster outskirts
\item calculate the synchrotron radio emission from radio relic
\end{itemize}

\subsection{CR protons}
The CR protons in the simulations are represented by a one-dimensional
isotropic distribution function \footnote{The three dimensional
  distribution function is given by $4\pi \int f(\gam)\, \gam^2\, \dd \gam$.}
given by
\begin{equation}
  \label{eq:f_p}
  f_\p(\gap) = \frac{\dd^2 N_\p}{\dd \gap\,\dd V} = 
  C\, \gap^{-\alpha}\,\theta(\gap-q)\,, 
\end{equation}
and the Lorentz factor $\gap \approx P_\p/m_\p c$, where we have
normalized the proton momentum $P_\p$ with the proton mass
$m_\p$. Here $q$ is the mass normalized momentum cutoff, $\alpha$ the
spectral index, and $C$ the normalization of the distribution function
in units of density.

To improve the numerical efficiency of the simulations the CR proton
distribution function is parameterized in terms of adiabatic invariant
momentum cutoff $q_0$ and the adiabatic invariant Lagrangian amplitude
of the spectrum $\tilde{C}_0$. We convert the adiabatic invariant
quantities to physical quantities through
\begin{equation}
  \label{eq:q0}
  q=\left(\frac{\rho}{\rho_0}\right)^{\frac{1}{3}}q_0\,,
\end{equation}
and
\begin{equation}
  \label{eq:C0}
  \tilde{C}=\left(\frac{\rho}{\rho_0}\right)^{-\frac{\alpha-1}{3}}\tilde{C}_0\,,
\end{equation}
where the convenient unitless redefinition of the CR proton amplitude
is given by
\begin{equation}
  \label{eq:Ct}
  \tilde{C}=C\,m_\p/\rho\,.
\end{equation}

@@

The CR electron distribution function can not be derived directly from
the CR protons because of the different timescales of loss
processes. Instead we first need to derive the injected CR proton
distribution function between each snapshot.  The injected
distribution function is calculated as the change in CR normalization
between a snapshot at time $t$ and an earlier time $t-\Delta t$:
\begin{eqnarray}
  \label{eq:finj}
f_\rmn{inj,p}(t,\gap) &=& \Delta C_0(t)\,\frac{\rho}{m_\p}\,
\gap^{-\alpha}\,,\qquad\rmn{where}\\
  \Delta  C_-(t) &=& C_0(t) - C_0(t-\Delta t)\,.
\end{eqnarray}
The time between snapshots is denoted by $\Delta t$ and is shown in
Table~\ref{tab:cluster_sample} for each simulated cluster. Note that
for most clusters we can not resolve the cooling timescale of CR
electrons, and hence we over estimate the abundance of electrons for
low and high momenta for some clusters (see
Figure~\ref{fig:e_spec_tests} for more details). Although, in the
region between $\gamma \sim (10-10^3)$ is small enough to resolve the
cooling processes.

@@

@@

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
  \includegraphics[width=0.49\columnwidth]{./figures/CRspec.alphaCheck.eps}
  \includegraphics[width=0.49\columnwidth]{./figures/CRspec.snapCheck.eps}
  \caption{Testing the robustness of the CR electron spectra. Left
    panel shows how different cuts in injected spectra impact the
    total volume weighted CR electron spectrum with full cooling; no
    spectral cut (red line), cut particles with $\alpha_\inj>2.2$
    (yellow line), cut particles with $\alpha_\inj>2.4$ (green line),
    cut particles with $\alpha_\inj>2.6$ (blue line). Note that in the
    main CR model we cut all particles with an $\alpha_\inj>2.4$,
    which is a factor four smaller at low energies than the spectrum
    without a cut. Right panel shows the effect of time-resolution on
    the CR electron spectra. The median CR spectrum is shown with full
    cooling that includes radiative, Coulomb, and adiabatic losses
    (dash-dotted line), the solid line represents the total volume
    weighted CR electron spectrum with full cooling. The three line
    colors corresponds to the same cluster, a large coma like merging
    cluster, but with different time resolution between snapshots in
    the relevant regime; red lines corresponds to 100 Myrs between
    snapshots, orange lines corresponds to ~(1.0-1.5) Gyrs between
    snapshots, and the blue lines corresponds to ~(1.0-1.5) Gyrs
    between snapshots. \label{fig:e_spec_tests}}
\end{minipage}
\end{figure*}

@@

\begin{figure}
  \includegraphics[width=1.0\columnwidth]{./figures/CRespec.all.1.4Rv.a24.full.020.v20.eps}
  \caption{Cosmic ray electron spectra in cluster outskirts at
    redshift zero. We show the total volume weighted CR electron
    distribution function in the region between (1.3-1.5)$\rvir$ with
    full cooling that includes radiative, Coulomb, and adiabatic
    losses. The the thin grey lines show the spectra from individual
    clusters while the thick solid line shows the median of the
    spectra from all clusters. \label{fig:e_spec_all}}
\end{figure}

\begin{figure}
  \includegraphics[width=1.0\columnwidth]{./figures/old/CRespecRadial.Radial2Rv.a24.140.v16.eps}
  \caption{Spatial dependence of the cosmic ray electron spectra at
    redshift zero. We show the total volume weighted CR electron
    distribution function; a Coma like cluster (left panel), a massive
    cooling flow cluster (middle panel), and the median of our 14
    cluster's spectra (right panel). The different line colors show
    the CR electron spectra for different radial
    bins.\label{fig:e_spec_spatial}}
\end{figure}

>>>>

\def\del#1{{}}
%\def\del#1{{\bf (DELETED TEXT)}}
%\def\C#1{#1}
\def\AP#1{{\bf AP: #1}}
\def\SPO#1{{\bf SPO: #1}}
\def\CP#1{{\bf CP: #1}}

@@

However, this then presents a puzzle. Cosmological simulations show that while gas initially undergoes strong shocks (up to $\mach \sim 10^{3}$) accreting onto non-linear structures and filaments, shocks in the ICM and cluster outskirts are relatively modest ($\mach \sim 1-5$), since the gas has already reached sub-keV temperatures \citep{ryu03,pfrommer06,skillman08}. While DSA is efficient in accelerating particles in the thermal Maxwellian tail at high Mach numbers \citep{bell78,drury83}, and as confirmed in observations of supernova remnants \citep{parizot06,reynolds08}, at lower Mach numbers the efficiency of DSA is known to plummet exponentially \SPO{should we include a figure of this? To me this paper is motivated by 2 figures, that of the acceleration efficiency as a function of Mach number and the cooling time as a function of energy---we could put it in 1 figure.} Indeed, in the test-particle regime where suprathermal particles undergo acceleration via a thermal leakage process (which compare well against kinetic DSA simulations) the acceleration efficiency for weak shocks $\mach \sim 3$ is extremely small; the fraction of protons accelerated is $\sim 10^{-4}-10^{-3}$, and cosmic ray proton pressure is $\lsim 1\%$ of the shock ram pressure \citep{kang11}. The acceleration efficiency of electrons at low Mach numbers is likely to be far smaller still. The injection problem for thermal electrons already known to be severe at high Mach numbers, due to the smaller gyroradius of thermal electrons: the relative acceleration efficiency of cosmic ray electrons is lower by $\sim 10^{-2}$ as in the Galaxy \citep{schlickeiser02} or even $\sim 10^{-4}$ as in supernova remnants \citep{morlino09}. These relative efficiencies likely plummets further at low Mach numbers. These considerations appear to contradict the appearance of bright radio relics, and perhaps suggest that our understanding of DSA at low Mach numbers is incomplete \citep[for recent progress, see][]{gargate12}.

A possible solution is if there is a pre-existing population of cosmic ray electrons with gyroradii comparable or larger than that of the shock thickness. In this case, injection from the thermal pool is no longer an issue \citep{markevitch05,giacintucci08,kang11}; here, \citet{kang11} show that re-acceleration should dominate over fresh injection. %\footnote{Turbulent re-acceleration, which is thought to operate at lower Mach numbers, also requires a seed population of relativistic particles}. 
DSA has a much larger effect on radio emission than adiabatic compression; including the downstream magnetic field amplification, synchrotron emission could be boosted by a factor $\sim 100-1000$ for $\mach \sim 3$ \citep{kang11}. Thus, the luminosity function of radio gischt will be strongly modified by the presence or absence of a seed relativistic electron population, whose existence has never been directly demonstrated. In this paper, we use our existing high-resolution SPH simulations of cosmic-ray protons in clusters \citep{pinzke10} to infer whether structure formation shocks could generate them\footnote{They could also have a non-gravitational origin, such as AGN injection, though the filling factor at these large radii is likely to be small.}, taking into account the effects of electron cooling. Note that DSA operates identically on relativistic particles of the same rigidity ($R=pc/Ze$), so the injected proton and electron spectrum are the same, modulo their relative acceleration efficiency, which we conservatively calibrate off Galactic observations.%\footnote{Note, however, that at energies where protons are subrelativistic, the electron spectrum has to be obtained from the proton spectrum by extrapolating the latter from the relativistic regime.} 
In the low-density outskirts of clusters, proton loss timescales are several Hubble times, so we can directly derive the injected energy to each SPH CRp particle directly from our existing simulation snapshots and derive an appropriate scaled injection of CR electrons (CRe). Unlike CRp, Coulomb and inverse Compton/synchrotron loss processes are more efficient and have to be taken into account (IC off the CMB, which has an equivalent energy density of $B_\CMB=3.24 (1+z)^{2} \mu$G, should dominate in the outer regions). We evolve the time-dependent cosmic-ray energy equation to track the evolving distribution function of CRe. In Fig~\ref{fig:ensslin}, we can see that the $\sim 10$ GeV CRe responsible for $\sim$GHz emission in a $\mu$G field has energy loss timescales of $\sim 10^{8}$yr, but a large population of $\sim 100$ MeV electrons could build up. Note that secondary CRe which arise from hadronic interactions of CRp are not thought to be significant at these low densities, though for a dissenting view, see \citet{keshet10}. We calculate the abundance of such seed electrons from structure formation shocks in the cluster outskirts. In general, we find that they are, reaffirming radio gischt as a reliable tracer of large scale shocks and magnetic fields

\begin{figure}%[ht]
\begin{center}
\resizebox{!}{5.5cm}{\includegraphics{./figures/timescales.eps}}
%%\resizebox{!}{5.5cm}{\includegraphics{ensslin2.pdf}}
%\resizebox{!}{5.0cm}{\includegraphics{circles.pdf}}
%%\hspace{0.05cm}
%%%\vspace{-1cm} 
\end{center}
\caption{Cooling time of CR electrons (left panel) and CR protons (right panel) for typical conditions in the ICM. CRe can only survive for a Hubble time in the underdense outskirts of clusters; $\sim 100$MeV electrons should be the most long-lived. By contrast, CRp above 10 GeV can survive on cosmological timescales. From \citet{ensslin11}. \SPO{I stole this figure from Ensslin Éshould we make our own?}}
\label{fig:ensslin} % caption for the whole figure
\end{figure}

\begin{figure}%[ht]
\begin{center}
\resizebox{!}{5.5cm}{\includegraphics{./figures/etamax.eps}}
\end{center}
\caption{Acceleration efficiency as a function of Mach number and
  spectral index. Need to remake figure, smaller Mach number range,
  fewer lines.}
\label{fig:etamax} 
\end{figure}

@@

\section{Simulations}
\label{sect:simulations}
Our simulations were performed in a $\Lambda$CDM universe using the
cosmological parameters: $\Omega_{\mr m}=\Omega_\DM + \Omega_{\mr
  b}=0.3, \, \Omega_{\mr b}=0.039, \, \Omega_\Lambda=0.7, \, h=0.7, \,
n_{\mr s}=1$, and $\sigma_8=0.9$. The total matter density in units of
the critical density of the universe $\rho_{\rm crit}$ is denoted by
$\Omega_{\mr m}$, the baryonic density by $\Omega_{\mr b}$, the DM
density by $\Omega_\DM$ and the cosmological constant today is denoted
by $\Omega_\Lambda$. The critical density, $\rho_{\rm crit}=3H_0/(8\pi
G)$, where the present day Hubble constant $H_0=100\, h \, \mr{km}\,
\mr{s}^{-1} \, \mr{Myr}^{-1}$. $n_{\mr s}$ represents the spectral
index of the primordial power-spectrum, and $\sigma_8$ denotes the
$rms$ linear mass fluctuation within a sphere of radius $8 \,h^{-1}
\mr{Mpc}$ extrapolated to $z = 0$. The simulations were carried out
with an updated and extended version of the distributed-memory
parallel TreeSPH code GADGET-2 \citep{2005MNRAS.364.1105S,
  2001NewA....6...79S}. Gravitational forces were computed using a
combination of particle-mesh and tree algorithms.  Hydrodynamic forces
are computed with a variant of the smoothed particle hydrodynamics
(SPH) algorithm that conserves energy and entropy where appropriate,
i.e. outside of shocked regions \citep{2002MNRAS.333..649S}.  Our
simulations follow the radiative cooling of the gas, star formation,
supernova feedback, and a photo-ionizing background \citep[details can
  be found in][]{2007MNRAS.378..385P}. We model the cosmic ray (CR)
physics in a self-consistent way \citep{pfrommer06,
  2007A&A...473...41E, 2008A&A...481...33J} and attach a CR proton
distribution function to each SPH fluid element. We include the
adiabatic CR transport process such as compression and rarefaction,
and a number of physical source and sink terms which modify the cosmic
ray pressure of each CR population separately. The most important
sources considered for injection are, diffusive shock acceleration at
cosmological structure formation shocks and shock waves in supernova
remnants, while the primary sinks are thermalization by Coulomb
interactions, and catastrophic losses by hadronization. For
simplicity, in this paper we do not take into account CRs injected
into the inter-stellar medium from supernova remnants. Although, note
that the contribution from the CR electrons that are accelerated in
supernova remnants is expected to be negligible compared to the CR
electron population the ICM, because of the much shorter cooling times
associated with the remnants. IS THIS TRUE? \del{(see Pinzke, Oh, and
  Pfrommer, in prep. for a discussion of this topic).}

@@

\section{Method}
\label{sect:method}
In this section we explain both the method that we use to derive the
CR electron distribution function that builds up during the structure
formation process of galaxy clusters, and the formalism for
calculating synchrotron emission from galaxy clusters that are
undergoing a merger at low redshifts.

Our scheme is summarized, in order, by the following bullet points:
\begin{itemize}
\item derive CR proton distribution function from each simulation
  output at different time $t$
\item calculate injected CR proton population between snapshots 
\item convert injected protons to injected electrons
\item evolve each injected CR electron population to a later time
  $\tend$ while accounting for losses (Coulomb, inverse Compton, and
  adiabatic)
\item add up the CR electron distribution for all SPH particles at time $\tend$
\item re-accelerate CR electron distribution function at time $\tend$
  using typical values for a merging shock in cluster outskirts
\item calculate the synchrotron radio emission from radio relic
\end{itemize}

\subsection{CR protons}
The CR protons in are represented by an isotropic one-dimensional
power-law distribution function \footnote{The three-dimensional
  distribution function is given by $4\pi \int f(\gam)\, \gam^2\, \dd
  \gam$.}  given by
\begin{equation}
  \label{eq:f_p}
  f_\p(\gap) = \frac{\dd^2 N_\p}{\dd \gap\,\dd V} = 
  C\, \gap^{-\alpha}\,\theta(\gap-q)\,, 
\end{equation}
and the Lorentz factor $\gap \approx P_\p/m_\p c$, where we have
normalized the proton momentum $P_\p$ with the proton mass
$m_\p$. Here $q$ is the proton mass normalized momentum cutoff,
$\alpha$ the spectral index, and $C$ the normalization of the
distribution function in units of density.

To improve the numerical efficiency of our simulations the CR proton
distribution function is parameterized in terms of adiabatic invariant
momentum cutoff $q_0$ and the adiabatic invariant Lagrangian amplitude
of the spectrum $\tilde{C}_0$. We convert the adiabatic invariant
quantities to physical quantities through
\begin{equation}
  \label{eq:q0}
  q=\left(\frac{\rho}{\rho_0}\right)^{\frac{1}{3}}q_0\,,
\end{equation}
and
\begin{equation}
  \label{eq:C0}
  \tilde{C}=\left(\frac{\rho}{\rho_0}\right)^{-\frac{\alpha-1}{3}}\tilde{C}_0\,,
\end{equation}
where the convenient unitless redefinition of the CR proton amplitude
is given by
\begin{equation}
  \label{eq:Ct}
  \tilde{C}=C\,m_\p/\rho\,.
\end{equation}

@@

The CR electron distribution function can not be derived directly from
the CR protons because of the different injection efficiencies and the
timescales of loss processes. Instead we first need to derive the
injected CR proton distribution function between each snapshot.  The
injected distribution function is calculated as the change in CR
normalization between a snapshot at time $t$ and an earlier time
$t-\Delta t$:
\begin{eqnarray}
  \label{eq:finj}
f_\rmn{inj,p}(t,\gap) &=& \Delta C_0(t)\,\frac{\rho}{m_\p}\,
\gap^{-\alpha}\,,\qquad\rmn{where}\\
  \Delta  C_-(t) &=& C_0(t) - C_0(t-\Delta t)\,.
\end{eqnarray}
The time between snapshots is denoted by $\Delta t$ and is shown in
Table~\ref{tab:cluster_sample} for each simulated cluster. Note that
for most clusters we can not resolve the cooling timescale of CR
electrons, and hence we over estimate the abundance of electrons for
low- and high-momenta for some clusters (see
Figure~\ref{fig:e_spec_tests} for more details). Although, in the
region between $\gamma \sim (3-5\times10^2)$ the typical cooling times
are small enough to be resolved by our simulations.

@@

\begin{figure}
  \includegraphics[width=1.0\columnwidth]{./figures/CRespec.all.1.4Rv.a24.full.020.v20.eps}
  \caption{Cosmic ray electron spectra in cluster outskirts at
    redshift zero. We show the total volume weighted CR electron
    distribution function in the region between (1.3-1.5)$\rvir$ with
    full cooling that includes radiative, Coulomb, and adiabatic
    losses. The the thin grey lines show the spectra from individual
    clusters while the thick solid line shows the median of the
    spectra from all clusters. Note that the CR spectra peaks at
    $\gamma \sim 30$ for all clusters (\AP{check cooling times}, and
    that there is about a factor 50 difference in the spectra between
    a large merging cluster and a small cool core cluster in the
    regime $\gamma_\e \sim (3,300)$. \label{fig:e_spec_all}}
\end{figure}

@@

@@

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
  \includegraphics[width=0.49\columnwidth]{./figures/CRspec.alphaCheck.eps}
  \includegraphics[width=0.49\columnwidth]{./figures/CRspec.snapCheck.eps}
  \caption{Testing the robustness of the CR electron spectra. Left
    panel shows how different cuts in injected spectra impact the
    total volume weighted CR electron spectrum with full cooling; no
    spectral cut (red line), cut particles with $\alpha_\inj>2.2$
    (yellow line), cut particles with $\alpha_\inj>2.4$ (green line),
    cut particles with $\alpha_\inj>2.6$ (blue line). Note that in the
    main CR model we cut all particles with an $\alpha_\inj>2.4$,
    which is a factor four smaller at low energies than the spectrum
    without a cut. Right panel shows the effect of time-resolution on
    the CR electron spectra. The median CR spectrum is shown with full
    cooling that includes radiative, Coulomb, and adiabatic losses
    (dash-dotted line), the solid line represents the total volume
    weighted CR electron spectrum with full cooling. The three line
    colors corresponds to the same cluster, a large coma like merging
    cluster, but with different time resolution between snapshots in
    the relevant regime; red lines corresponds to 100 Myrs between
    snapshots, orange lines corresponds to ~(1.0-1.5) Gyrs between
    snapshots, and the blue lines corresponds to ~(1.0-1.5) Gyrs
    between snapshots. \AP{Do we want to put these figures in an
      appendix?} \label{fig:e_spec_tests}}
\end{minipage}
\end{figure*}

\begin{figure}
  \includegraphics[width=1.0\columnwidth]{./figures/old/CRespecRadial.Radial2Rv.a24.140.v16.eps}
  \caption{Spatial dependence of the cosmic ray electron spectra at
    redshift zero. We show the total volume weighted CR electron
    distribution function; a Coma like cluster (left panel), a massive
    cooling flow cluster (middle panel), and the median of our 14
    cluster's spectra (right panel). The different line colors show
    the CR electron spectra for different radial bins. \AP{We might
      want to put this type of figure in the second
      paper!?!}\label{fig:e_spec_spatial}}
\end{figure}
